On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-10-22 paper.tex
Update about to-do graph

***Maybe a graph comparing maximum and average. Or compute/plot their ratio. The asymptotic slopes are $\sqrt(1/a^2+1/b^2)$ for $\funt$ and $2/\pi(1/a+1/b)$. It may be interesting to consider the ratio of asymptotic slopes, as a function of $a/b$. It is maximum for $a=b$, and equals $2\sqrt 2/\pi = 0.9003$. It tends to $2/\pi$ for $a/b \rightarrow \infty$ and for $a/b \rightarrow 0$. The minimum number of tiles that can be visited with non-zero probability (corresponding to an n times 1 discrete bounding rectangle if a>=b) can also be plotted.

>>>>

***Graph of asymptotic slopes: $\sqrt(1/a^2+1/b^2)$ for $\funt$ and $2/\pi(1/a+1/b)$. It may be interesting to consider the ratio of asymptotic slopes, as a function of $a/b$. It is maximum for $a=b$, and equals $2\sqrt 2/\pi = 0.9003$. It tends to $2/\pi$ for $a/b \rightarrow \infty$ and for $a/b \rightarrow 0$.
